The core transcriptome of mammalian placentas and the divergence of expression with placental shape

### 2016-11-30 manuscript/manuscript.Rnw
mention classification when they are discussed
add another digit to output

<<load.libraries,echo=FALSE,results="hide",warning=FALSE,message=FALSE,error=FALSE,cache=FALSE>>=
opts_chunk$set(dev="cairo_pdf",out.width="\\columnwidth",out.height="0.7\\textheight",out.extra="keepaspectratio")
opts_chunk$set(cache=TRUE, autodep=TRUE)
options(device = function(file, width = 8, height = 7, ...) {
  cairo_pdf(tempfile(), width = width, height = height, ...)
})
options(scipen = -2, digits = 0)
library("data.table")
library("ggplot2")
library("reshape2")
library("xtable")
library("grid")
library("gridExtra")
library("ape")
library("ggtree")
library("RSQLite")
library("topGO")
library("org.Hs.eg.db")
library("scales")
library("magrittr")
library("tidyr")
library("phytools")
@

@@

We correlated different aspects of placenta morphology, including
shape, intimacy, and interdigitation with the mRNA transcription
profiles of all 1:1 human orthologs with \ac{FPKM} greater than 10 in
one species, and \ac{FPKM} greater than 1 at least two species.

@@

>>>>

<<load.libraries,echo=FALSE,results="hide",warning=FALSE,message=FALSE,error=FALSE,cache=FALSE>>=
opts_chunk$set(dev="cairo_pdf",out.width="\\columnwidth",out.height="0.7\\textheight",out.extra="keepaspectratio")
opts_chunk$set(cache=TRUE, autodep=TRUE)
options(device = function(file, width = 8, height = 7, ...) {
  cairo_pdf(tempfile(), width = width, height = height, ...)
})
options(scipen = -2, digits = 1)
library("data.table")
library("ggplot2")
library("reshape2")
library("xtable")
library("grid")
library("gridExtra")
library("ape")
library("ggtree")
library("RSQLite")
library("topGO")
library("org.Hs.eg.db")
library("scales")
library("magrittr")
library("tidyr")
library("phytools")
@

@@

We correlated different aspects of placenta morphology, including
shape, intimacy, and interdigitation with the mRNA transcription
profiles of all 1:1 human orthologs with \ac{FPKM} greater than 10 in
one species, and \ac{FPKM} greater than 1 at least two species.
Supplemental \cref{tab:placental_classification} lists the shape,
intimacy, and interdigitiation of each species analyzed.

@@

\DLA{They're in the first paragraph of the introduction, but I've also
  referred to them now in the first subsection here.}
